Dependently Typed Multi-stage Calculus

### 2019-11-30 slides/main.tex
Fix.
Making speach draft.

    \tableofcontents
    \note{
    }
\end{frame}

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm that enables
    \begin{itemize}
        \item Generation of code at run-time
        \item Evaluation of code at run-time
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using run-time information \\
            (a.k.a. run-time specialization)
        \item DSLs
    \end{itemize}
    \note{
        a.k.a = Also known as
    }
\end{frame}

@@

\begin{frame}[fragile]{Kinding rules of \LMD}
    Kiding judgements also inculde stages.
    \begin{center}
        \( \G \vdash \tau :: K @ n \)
    \end{center}
    Types have also stages because types may contains terms.
    \begin{center}
    {\footnotesize
    \infrule[{\KApp}]{
        \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
    }{
        \G\V \sigma\ M::K[x\mapsto M] @ n
    }
    \infrule[{\KAbs}]{
        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
    }{
        \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
    }}
    \end{center}
\end{frame}

>>>>

    \tableofcontents
    \note{
        Thank you for coming. I am Akira Kawata at Graduate School of
        Informatics, Kyoto University. Today, I talk about Dependently Typed
        Multi-stage Calculus.

        This is today's outline. Firstly, I will introduce multi-stage
        programming paradigm. Secondly, I explain existing multi-stage
        calculus lambda-triangle-percent, which I call it lambda-T-P from now
        because lambda-triangle-present is quite long. Lastly, I talk about
        lambda-M-D which is an extension of lambda-T-P with dependent types.
    }
\end{frame}

\begin{frame}[fragile]{What is Multi-stage Programming}
    A programming paradigm that enables
    \begin{itemize}
        \item Generation of code at run-time
        \item Evaluation of code at run-time
    \end{itemize}
    Applications
    \begin{itemize}
        \item Speeding up programs using run-time information \\
            (a.k.a. run-time specialization)
        \item DSLs
    \end{itemize}
    \note{
        So, what is multi-stage programming? It is a programming paradigm that
        enables generation of code at run-time and evaluation of code at
        run-time simultaneously. Famous applications of multi-stage programming
        is speeding up programs using run-time information, which is also known
        as run-time specialization and DSLs, for example TODO.
    }
\end{frame}

@@

\begin{frame}[fragile]{Kinding rules of \LMD}
    Kiding judgements also include stages.
    \begin{center}
        \( \G \vdash \tau :: K @ n \)
    \end{center}
    Because types may contains terms. (e.g. vec n)
    \begin{center}
    {\footnotesize
    \infrule[{\KApp}]{
        \G\V \sigma:: (\Pi x:\tau.K) @ n \andalso \G\V M:\tau @ n
    }{
        \G\V \sigma\ M::K[x\mapsto M] @ n
    } \\[2mm]
    \infrule[{\KAbs}]{
        \G\V \tau :: * @ n \andalso \G,x:\tau@ n \V \sigma::J@A
    }{
        \G\V(\Pi x:\tau.\sigma) :: (\Pi x:\tau.J) @ n
    }}
    \end{center}
\end{frame}
